A Cross-Domain Benchmark for Active Learning

### 2024-06-03 doc/al_benchmark_paper.tex
Some english stuff

Active Learning (AL) deals with identifying the most informative samples for
labeling to reduce data annotation costs for supervised learning tasks. AL
research suffers from the fact that lifts from literature generalize poorly and
are only conducted on a small number of repetitions of experiments. To overcome
this obstacles, we propose \emph{ALBench}, the first active learning benchmark
which includes tasks in computer vision, natural language processing and tabular
learning. Furthermore, by providing an efficient greedy oracle, \emph{ALBench}
can be evaluated with 50 runs for each experiment. We will show, that both the
cross-domain character and the large amount of repetitions are crucial for
sophisticated evaluation of AL research. Concretely, we will show that the
superiority of specific methods varies over the different domains, making it
important to evaluate Active Learning with a cross-domain benchmark.
Additionally, we show, that having a large amount of runs is crucial. With only
conducting five runs as often done in the literature, the superiority of
specific methods can strongly vary with the specific runs. This effect goes so
far, that it may even happen that dedicated methods like \emph{margin-sampling}
are not able to outperform the random baseline.
\end{abstract}

>>>>

Active Learning (AL) deals with identifying the most informative samples for
labeling to reduce data annotation costs for supervised learning tasks. AL
research suffers from the fact that lifts from literature generalize poorly and
that only a small number of repetitions of experiments are conducted. To overcome
this obstacles, we propose \emph{ALBench}, the first active learning benchmark
which includes tasks in computer vision, natural language processing and tabular
learning. Furthermore, by providing an efficient greedy oracle, \emph{ALBench}
can be evaluated with 50 runs for each experiment. We will show, that both the
cross-domain character and the large amount of repetitions are crucial for
sophisticated evaluation of AL research. Concretely, we will show that the
superiority of specific methods varies over the different domains, making it
important to evaluate Active Learning with a cross-domain benchmark.
Additionally, we show, that having a large amount of runs is crucial. With only
conducting five runs as often done in the literature, the superiority of
specific methods can strongly vary with the specific runs. This effect goes so
far, that it may even happen that dedicated methods like \emph{margin-sampling}
are not able to outperform the random baseline.
\end{abstract}
